\textbf{\supplement}\vskip 2ex \mytitle\vskip 2ex

### 2023-06-07 expanded-appendix.tex
Final updates for Computer Journal

% 
% This file has been expanded from LaTeX file (appendix.tex)
%   to make this straight forward LaTeX file (expanded-appendix.tex)
%     that depends on nothing (it inputs no files apart from the document class files).
%       Each required file's text was input in situ - search for % expand
% 
% (Otherwise the file appendix.tex would use BibTeX, a macro file, tables of contents, its own and the other files's .aux files, and includes various files in generated/*, etc.)
%

@@

@@

\@writefile{toc}{\contentsline {subsection}{\numberline {12.b}Pilot paper sample}{54}{subsection.12.2}\protected@file@percent }

@@

\@writefile{lot}{\contentsline {table}{\numberline {9}{\ignorespaces Sizes of repositories, with approximate sizes of code (in kLOC) and data for all available GitHub repositories reviewed in the survey, plus \texttt  {covid-sim} \cite  {ICmodel} for comparison. Sizes are approximate because in all repositories code and data are conceptually interchangeable (an issue explained in the Supplemental Material), so choices were made in the survey to avoid double-counting. Many repositories rely on downloading additional code and data, which is not counted in the table as the additional required material is not in the repository cited in the paper. At the time of cloning and checking all repositories in May 2023, paper [182]\ still had nothing in its repository except a single file still saying ``\ldots  \ code coming soon\nobreakspace  {}\ldots  ,'' despite 47\ months having already elapsed since the paper had claimed the code could be accessed in its repository.}}{55}{table.9}\protected@file@percent }

@@

@@

\@writefile{toc}{\contentsline {subsubsection}{\numberline {12.d.3}Problems of restrictive journal policies}{64}{subsubsection.12.4.3}\protected@file@percent }
\newlabel{supplement-restrictive-policies}{{12.d.3}{64}{Problems of restrictive journal policies}{subsubsection.12.4.3}{}}

@@

% read in any constants defined from the JSON or Git data
% expand generated/constants.tex
% Generated by programs/data.js
\def\journalBreakdown{\emph{Lancet Digital Health\/} ($N=6$), \emph{Nature Digital Medicine\/} ($N=12$) and \emph{Royal Society Open Science\/} ($N=14$)}
\def\tabularJournalBreakdown{&\hbox to 3em {\hfill 6}\hskip 1em \emph{Lancet Digital Health}\\&\hbox to 3em {\hfill 12}\hskip 1em \emph{Nature Digital Medicine}\\&\hbox to 3em {\hfill 14}\hskip 1em \emph{Royal Society Open Science}\\}
\global\newcount \dataN \global\dataN=32
\global\newcount \countAuthors \global\countAuthors=264
\global\newcount \countHasBreach \global\countHasBreach=11
\global\newcount \countHasPolicy \global\countHasPolicy=26
\global\newcount \countUsesVersionControlRepository \global\countUsesVersionControlRepository=10
\global\newcount \counthasDataRepository \global\counthasDataRepository=9
\global\newcount \countNoCodeInRepo \global\countNoCodeInRepo=1
\global\newcount \numberOfJournals \global\numberOfJournals=3
\global\newcount \countCodetested \global\countCodetested=0
\global\newcount \hasDevelopedRigorously \global\hasDevelopedRigorously=0
\global\newcount \countFields \global\countFields=36
\global\newcount \countCommentedOut \global\countCommentedOut=7
\global\newcount \countNotCommentedOut \global\countNotCommentedOut=2
\global\newcount \countMissingCode \global\countMissingCode=1
\global\def \averagePagesPerAuthor{1.2916666666666667}
% end expanding generated/constants.tex
% expand generated/metadata.tex
% shell script (make-metadata.sh) generated LaTeX variable values counting errors detected by data.js
\newcount \JSONerrorCount
\JSONerrorCount = 30
\newcount \dataVariableCount
\dataVariableCount = 63
% end expanding generated/metadata.tex
% expand generated/covidsimSummary.tex
% data calculated from the Ferguson covid-sim repo
\def \covidsimkLOC {25}
\def \covidsimfiles {229}
\def \covidsimdata{734 Mb}
% end expanding generated/covidsimSummary.tex
% expand generated/clone-date.tex
% date generated by running generated/allGitRepos.sh downloading Git repos
\def\clonedate {\ignorespaces 25 May 2023}
\def\cloneyear {2023}
\def\clonemonth {05}
% end expanding generated/clone-date.tex

@@

\contentsline {subsection}{\numberline {12.b}Pilot paper sample}{54}{subsection.12.2}%

@@

\contentsline {subsubsection}{\numberline {12.d.3}Problems of restrictive journal policies}{64}{subsubsection.12.4.3}%

@@

\texttt{make all}&
      Analyze the data, then typeset the main PDF files (\texttt{paper-seb-main.pdf} and \texttt{paper-seb-supplementary-material.pdf}).\\
   \multicolumn{1}{l@{\vdots}}{}&\\

@@

\texttt{make git-prep}&
      What's on Git that we've lost, or stuff we have got locally but probably don't want on Git, so you can delete it or move it out the way or whatever.\\
   \multicolumn{1}{l@{\vdots}}{}&\\

\texttt{make really-tidyup}&
      More thorough than \texttt{make tidyup} --- remove \emph{all} files that can be recreated. (This will mean next time you run \LaTeX\ you will have to ignore errors as the .aux files are re-created.)\\
\end{tabular}}

@@

\cite{ref-14} & Data directly written into program code.\flagStyle{ } & Basic Matlab with routine comments.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_0$\hskip 3pt{}}\\

@@

\bibitem{science-lancet1}
Servick, K. and Enserink, M. (2020) ``A mysterious company's coronavirus papers
  in top medical journals may be unraveling,'' {\em Science}.
\newblock \doi{10.1126/science.abd1337}

@@

\bibitem{jvs1}
Hardouin, S., Cheng, T.~W., Mitchell, E.~L., Raulli, S.~J., Jones, D.~W.,
  Siracuse, J.~J. and Farber, A. (2020) ``Prevalence of unprofessional social
  media content among young vascular surgeons,'' {\em Journal of Vascular
  Surgery}, \textbf{72}(2):667--671.
\newblock \doi{10.1016/j.jvs.2019.10.069}

@@

\bibitem{swebok}
Bourque, P. and Fairley, R., eds. (2014) {\em Guide to the Software Engineering
  Body of Knowledge}, (Version 3.0), IEEE Computer Society.
\newblock \url{www.swebok.org}

@@

\bibitem{differential-equations}
Boldo, S., Cl{\'{e}}ment, F., Filli{\^{a}}tre, J.-C., Mayero, M., Melquiond, G.
  and Weis, P. (2014) ``Trusting computations: {A} mechanized proof from
  partial differential equations to actual program,'' {\em Computers and
  Mathematics with Applications}, \textbf{68}:325--352.
\newblock \doi{10.1016/j.camwa.2014.06.004}

\bibitem{numerals}
Thimbleby, H. and Cairns, P. (2017) ``Interactive numerals,'' {\em Royal
  Society Open Science}, \textbf{4}(4):160903.
\newblock \doi{10.1098/rsos.160903}

@@

\bibitem{plos}
Chao, D.~L., Halloran, M.~E., Obenchain, V.~J. and {Longini Jr}, I.~M. (2010)
  ``{FluTE}, a publicly available stochastic influenza epidemic simulation
  model,'' {\em PLOS Computational Biology}, \textbf{6}(1):e1000656.
\newblock Source code available at \url{GitHub.com/dlchao/FluTE},
  \doi{10.1371/journal.pcbi.1000656}

\bibitem{excel1}
Abir, M., Nelson, C., Chan, E.~W., Al-Ibrahim, H., Cutter, C., Patel, K. and
  Bogart, A. (2020) {\em {RAND} Critical Care Surge Response Tool: {An}
  Excel-Based Model for Helping Hospitals Respond to the {COVID-19} Crisis},
  RAND Corporation.
\newblock
  \url{www.rand.org/}\midurl{pubs/}\midurl{tools/}\midurl{TLA164-}\midurl{1.html}

\bibitem{excel2}
Alvarez, N.~M., Gonzalez-Gonzalez, E. and Trujillo-de Santiago, G. (2020)
  ``Modeling {COVID-19} epidemics in an excel spreadsheet: {Democratizing} the
  access to first-hand accurate predictions of epidemic outbreaks,'' {\em
  MedRxiv}.
\newblock Preprint, \doi{10.1101/2020.03.23.20041590}

@@

\bibitem{hci1}
Shneiderman, B., Plaisant, C., Cohen, M. and {\emph{et al}} (2016) {\em
  Designing the User Interface: Strategies for Effective Human-Computer
  Interaction}, Pearson, 6th~ed.
\newblock \url{www.cs.umd.edu/}\midurl{hcil/}\midurl{DTUI6}

@@

\bibitem{flexibility}
Hanson, C. and Sussman, G.~J. (2021) {\em Software design for flexibility: How
  to avoid programming yourself into a corner}, MIT Press.

@@

\bibitem{peerReview}
Baum, T., {Le\ss mann}, H. and Schneider, K. (2017) ``The choice of code review
  process: A survey on the state of the practice,'' {\em in Lecture Notes in
  Computer Science}, vol.~\textbf{10611} of Product-Focused Software Process
  Improvement: 18th International Conference, pp.~111--127.
\newblock \doi{10.1007/978-3-319-69926-4_9}

\bibitem{ssi-report}
Brett, A., Croucher, M., Haines, R., Hettrick, S., Hetherington, J., Stillwell,
  M. and Wyatt, C. (2017) {\em State of the Nation Report for Research Software
  Engineers}, Research Software Engineer Network.
\newblock \url{zenodo.org/}\midurl{record/}\midurl{495360#.Xyfuyi2ZOCM},
  \doi{10.5281/zenodo.495360}

@@

\bibitem{cyber-cacm}
Shostack, A. and Zurko, M.~E. (2020) ``Secure development tools and techniques
  need more research that will increase their impact and effectiveness in
  practice,'' {\em Communications of the ACM}, \textbf{63}(5):39--41.
\newblock \doi{10.1145/3386908}

@@

\bibitem{electronic-evidence}
Mason, S. and Seng, D. (2017) {\em Electronic Evidence}, Humanities Digital
  Library, 4th~ed.
\newblock (NB See
  \url{humanities-digital-library.org/index.php/hdl/catalog/book/electronicevidence}
  until DOI is resolved), \doi{10.14296/517.9781911507079}

\bibitem{simon-artificial}
Simon, H.~A. and Laird, J. (2019) {\em Sciences of the Artificial}, MIT Press,
  3rd~ed.

\bibitem{dunning-kruger}
Kruger, J. and Dunning, D. (1999) ``Unskilled and unaware of it: {How}
  difficulties in recognizing one's own incompetence lead to inflated
  self-assessments,'' {\em Journal of Personality and Social Psychology},
  \textbf{77}(6):1121--1134.
\newblock \doi{10.1037/0022-3514.77.6.1121}

\bibitem{dunning-kruger-numeracy}
Nuhfer, E., Fleisher, S., Cogan, C., Wirth, K. and Gaze, E. (2017) ``How random
  noise and a graphical convention subverted behavioral scientists'
  explanations of self-assessment data: {Numeracy} underlies better
  alternatives,'' {\em Numeracy}, \textbf{10}(1):4.
\newblock \doi{10.5038/1936-4660.10.1.4}

@@

\bibitem{viruses}
Thimbleby, H., Anderson, S.~O. and Cairns, P. (1999) ``A framework for
  modelling {Trojans} and computer virus infection,'' {\em Computer Journal},
  \textbf{41}(7):444--458.
\newblock \doi{10.1093/comjnl/41.7.444}

@@

\bibitem{lancet-retracted}
Mehra, M.~R., Desai, S.~S., Ruschitzka, F. and Patel, A.~N. (2020)
  ``{RETRACTED}: {Hydroxychloroquine} or chloroquine with or without a
  macrolide for treatment of {COVID}-19: {A} multinational registry analysis,''
  {\em The Lancet}, \textbf{{online}}:1--10.
\newblock \doi{10.1016/S0140-6736(20)31180-6}

\bibitem{fda}
Zhang, Y., Masci, P., Jones, P. and Thimbleby, H. (2019) ``User interface
  software errors in medical devices,'' {\em Biomedical Instrumentation {\&}
  Technology}, \textbf{53}(3):182--194.
\newblock \doi{10.2345/0899-8205-53.3.182}

\bibitem{stability}
Salama, M., Bahsoon, R. and Lago, P. (2021) ``Stability in software
  engineering: Survey of the state-of-the-art and research directions,'' {\em
  IEEE Transactions on Software Engineering}, \textbf{47}(7):1468--1510.
\newblock \doi{10.1109/TSE.2019.2925616}

@@

% expand generated/survey-references.bbl
% Generated by programs/data.js
\vbox{\bibitem{ref-1}
{\sc A. Callahan, E. Steinberg, J. A. Fries, S. Gombar, B. Patel, C. K. Corbin, and N. H. Shah}, ``Estimating the efficacy of symptom-based screening for COVID-19,'' \emph{Nature Digital Medicine}, \textbf{3}(95):3pp, 2020. DOI \texttt{10.1038/s41746-020-0300-0}\\\hfill{Accessed 14 July 2020.}\ {Double-checked 17 January 2021}.}\bibskip

\vbox{\maprepo{MetricSelectionFramework}\bibitem{ref-2}
{\sc C. M. Kanzler, M. D. Rinderknecht, A. Schwarz, I. Lamers, C. Gagnon, J. P. O. Held, P. Feys, A. R. Luft, R. Gassert, and O. Lambercy}, ``A data-driven framework for selecting and validating digital health metrics: use-case in neurological sensorimotor impairments,'' \emph{Nature Digital Medicine}, \textbf{3}(80):17pp, 2020. DOI \texttt{10.1038/s41746-020-0286-7} {Code \url{github.com/ChristophKanzler/MetricSelectionFramework}}\\\hfill{Accessed 14 July 2020.}\ {Double-checked 17 January 2021}.}\bibskip

\vbox{\bibitem{ref-3}
{\sc A. Roy, K. Nikolitch, R. McGinn, S. Jinah, W. Klement, and Z. A. Kaminsky}, ``A machine learning approach predicts future risk to suicidal ideation from social media data,'' \emph{Nature Digital Medicine}, \textbf{3}(78):12pp, 2020. DOI \texttt{10.1038/s41746-020-0287-6}\\\hfill{Accessed 14 July 2020.}\ {Double-checked 17 January 2021}.}\bibskip

\vbox{\bibitem{ref-4}
{\sc D. M. Levine, Z. Co, L. P. Newmark, A. R. Groisser, A. J. Holmgren, J. A. Haas, and D. W. Bates}, ``Design and testing of a mobile health application rating tool.,'' \emph{Nature Digital Medicine}, \textbf{3}(74):7pp, 2020. DOI \texttt{10.1038/s41746-020-0268-9}\\\hfill{Accessed 14 July 2020.}\ {Double-checked 17 January 2021}.}\bibskip

\vbox{\bibitem{ref-5}
{\sc T. Kannampallil, J. M. Smyth, S. Jones, P. R. O. Payne, and J. Ma}, ``Cognitive plausibility in voice-based AI health counselors,'' \emph{Nature Digital Medicine}, \textbf{3}(72):4pp, 2020. DOI \texttt{10.1038/s41746-020-0278-7}\\\hfill{Accessed 14 July 2020.}\ {Double-checked 17 January 2021}.}\bibskip

\vbox{\maprepo{PENet}\bibitem{ref-6}
{\sc S. Huang, T. Kothari, I. Banerjee, C. Chute, R. L. Ball, N. Borus, A. Huang, B. N. Patel, P. Rajpurkar, J. Irvin, J. Dunnmon, J. Bledsoe, K. Shpanskaya, A. Dhaliwal, R. Zamanian, A. Y. Ng, and M. P. Lungren}, ``PENet a scalable deep-learning model for automated diagnosis of pulmonary embolism using volumetric CT imaging,'' \emph{Nature Digital Medicine}, \textbf{3}(61):9pp, 2020. DOI \texttt{10.1038/s41746-020-0266-y} {Code \url{github.com/marshuang80/PENet}}\\\hfill{Accessed 14 July 2020.}\ {Double-checked 17 January 2021}.}\bibskip

\vbox{\bibitem{ref-7}
{\sc S. S. Dhruva, J. S. Ross, J. G. Akar, B. Caldwell, K. Childers, W. Chow, L. Ciaccio, P. Coplan, J. Dong, H. J. Dykhoff, S. Johnston, T. Kellogg, C. Long, P. A. Noseworthy, K. Roberts, A. Saha, A. Yoo, and N. D. Shah}, ``Aggregating multiple real-world data sources using a patient-centered health-data-sharing platform,'' \emph{Nature Digital Medicine}, \textbf{3}(60):9pp, 2020. DOI \texttt{10.1038/s41746-020-0265-z}\\\hfill{Accessed 14 July 2020.}\ {Double-checked 17 January 2021}.}\bibskip

\vbox{\maprepo{PostoperativeOutcomes.RiskNet}\bibitem{ref-8}
{\sc I. S. Hofer, C. Lee, E. Gabel, P. Baldi, and M. Cannesson}, ``Development and validation of a deep neural network model to predict postoperative mortality, acute kidney injury, and reintubation using a single feature set,'' \emph{Nature Digital Medicine}, \textbf{3}(58):10pp, 2020. DOI \texttt{10.1038/s41746-020-0248-0} {Code \url{github.com/cklee219/PostoperativeOutcomes_RiskNet}}\\\hfill{Accessed 14 July 2020.}\ {Double-checked 17 January 2021}.}\bibskip

>>>>

% Please do not edit this file, expanded-appendix.tex!
% It was generated automatically from its master file appendix.tex, by programs/expand.js
% Get everything from https://github.com/haroldthimbleby/improving-science
% 
% This file expands the LaTeX file (appendix.tex), which has complex dependencies,
%   to make this simple LaTeX file (expanded-appendix.tex)
%     that depends on nothing, apart from its standard document class.
%       This expanded file depends on no other files, as instead
%         each required file's text was input and expanded recursively - search for '% expand' in the expanded file below.
% 
% (The original file is dependent on BibTeX (.bst and .bbl files), a macro file, table of contents,
%   its own and other files' .aux files,
%     as well as various data files in the directory generated
%       etc. All these file dependencies have been removed.)
%

@@

\@writefile{toc}{\contentsline {subsection}{\numberline {12.b}Pilot paper sample}{53}{subsection.12.2}\protected@file@percent }

@@

@@

\@writefile{lot}{\contentsline {table}{\numberline {9}{\ignorespaces Sizes of repositories, with approximate sizes of code (in kLOC) and data for all available GitHub repositories reviewed in the survey, plus \texttt  {covid-sim} \cite  {ICmodel} for comparison. Sizes are approximate because in all repositories code and data are conceptually interchangeable (an issue explained in the Supplemental Material), so choices were made in the survey to avoid double-counting. Many repositories rely on downloading additional code and data, which is not counted in the table as the additional required material is not in the repository cited in the paper. At the time of cloning and checking all repositories in June 2023, paper [182]\ still had nothing in its repository except a single file still saying ``\ldots  \ code coming soon\nobreakspace  {}\ldots  ,'' despite 48\ months having already elapsed since the paper had claimed the code could be accessed in its repository.}}{55}{table.9}\protected@file@percent }

@@

\@writefile{toc}{\contentsline {subsubsection}{\numberline {12.d.3}Problems of restrictive journal policies}{63}{subsubsection.12.4.3}\protected@file@percent }
\newlabel{supplement-restrictive-policies}{{12.d.3}{63}{Problems of restrictive journal policies}{subsubsection.12.4.3}{}}

@@

@@

% read in any constants defined from the JSON or Git data
% expand generated/constants.tex
% Generated by programs/data.js
\def\journalBreakdown{\emph{Lancet Digital Health\/} ($N=6$), \emph{Nature Digital Medicine\/} ($N=12$) and \emph{Royal Society Open Science\/} ($N=14$)}
\def\tabularJournalBreakdown{&\hbox to 3em {\hfill 6}\hskip 1em \emph{Lancet Digital Health}\\&\hbox to 3em {\hfill 12}\hskip 1em \emph{Nature Digital Medicine}\\&\hbox to 3em {\hfill 14}\hskip 1em \emph{Royal Society Open Science}\\}
\global\newcount \dataN \global\dataN=32
\global\newcount \countAuthors \global\countAuthors=264
\global\newcount \countHasBreach \global\countHasBreach=11
\global\newcount \countHasPolicy \global\countHasPolicy=26
\global\newcount \countUsesVersionControlRepository \global\countUsesVersionControlRepository=10
\global\newcount \counthasDataRepository \global\counthasDataRepository=9
\global\newcount \countNoCodeInRepo \global\countNoCodeInRepo=1
\global\newcount \numberOfJournals \global\numberOfJournals=3
\global\newcount \countCodetested \global\countCodetested=0
\global\newcount \hasDevelopedRigorously \global\hasDevelopedRigorously=0
\global\newcount \countFields \global\countFields=36
\global\newcount \countCommentedOut \global\countCommentedOut=7
\global\newcount \countNotCommentedOut \global\countNotCommentedOut=2
\global\newcount \countMissingCode \global\countMissingCode=1
\global\def \averagePagesPerAuthor{1.2916666666666667}
% end expanding generated/constants.tex
% expand generated/metadata.tex
% shell script (make-metadata.sh) generated LaTeX variable values counting errors detected by data.js
\newcount \JSONerrorCount
\JSONerrorCount = 30
\newcount \dataVariableCount
\dataVariableCount = 62
% end expanding generated/metadata.tex
% expand generated/covidsimSummary.tex
% data calculated from the Ferguson covid-sim repo
\def \covidsimkLOC {25}
\def \covidsimfiles {229}
\def \covidsimdata{734 Mb}
% end expanding generated/covidsimSummary.tex
% expand generated/clone-date.tex
% date generated by running generated/allGitRepos.sh downloading Git repos
\def\clonedate {\ignorespaces 7 June 2023}
\def\cloneyear {2023}
\def\clonemonth {06}
% end expanding generated/clone-date.tex

@@

\contentsline {subsection}{\numberline {12.b}Pilot paper sample}{53}{subsection.12.2}%

@@

\contentsline {subsubsection}{\numberline {12.d.3}Problems of restrictive journal policies}{63}{subsubsection.12.4.3}%

@@

\texttt{make all}&
      Download and analyze the data, then typeset the main files (\texttt{paper.pdf}, \texttt{appendix.pdf} and \texttt{all.pdf}) that import all the data, as well as make the self-contained expanded \texttt{.tex} (and \texttt{.PDF}) files that do not depend on the separate data files in \texttt{data/*}.\\
   \multicolumn{1}{l@{\vdots}}{}&\\

@@

\texttt{make help}&
      Explain how to use \texttt{make}, and list all available options for using it.\\
\end{tabular}}

@@

\cite{ref-14} & Data directly written into program code.\flagStyle{ } & Basic Matlab with routine comments. Supplemental files Rsos192210supp1.docx and Rsos192210supp2.docx have links but were not accessible at time of double checking.\flagStyle{ $\sf P_c$\hskip 3pt{}$\sf P_{{\mbox{\scriptsize c-breach}}}$\hskip 3pt{}$\sf S_{+}$\hskip 3pt{}$\sf C_0$\hskip 3pt{}}\\

@@

\bibitem{science-lancet1}
Servick, K., and Enserink, M. (2020) ``A mysterious company's coronavirus
  papers in top medical journals may be unraveling,'' {\em Science}.
\newblock \doi{10.1126/science.abd1337}

@@

\bibitem{jvs1}
Hardouin, S., Cheng, T.~W., Mitchell, E.~L., Raulli, S.~J., Jones, D.~W.,
  Siracuse, J.~J., and Farber, A. (2020) ``Prevalence of unprofessional social
  media content among young vascular surgeons,'' {\em Journal of Vascular
  Surgery}, \textbf{72}(2):667--671.
\newblock \doi{10.1016/j.jvs.2019.10.069}

@@

\bibitem{swebok}
Bourque, P., and Fairley, R., eds. (2014) {\em Guide to the Software
  Engineering Body of Knowledge}, (Version 3.0), IEEE Computer Society.
\newblock \url{www.swebok.org}

@@

\bibitem{differential-equations}
Boldo, S., Cl{\'{e}}ment, F., Filli{\^{a}}tre, J.-C., Mayero, M., Melquiond,
  G., and Weis, P. (2014) ``Trusting computations: {A} mechanized proof from
  partial differential equations to actual program,'' {\em Computers and
  Mathematics with Applications}, \textbf{68}:325--352.
\newblock \doi{10.1016/j.camwa.2014.06.004}

\bibitem{numerals}
Thimbleby, H., and Cairns, P. (2017) ``Interactive numerals,'' {\em Royal
  Society Open Science}, \textbf{4}(4):160903.
\newblock \doi{10.1098/rsos.160903}

@@

\bibitem{plos}
Chao, D.~L., Halloran, M.~E., Obenchain, V.~J., and {Longini Jr}, I.~M. (2010)
  ``{FluTE}, a publicly available stochastic influenza epidemic simulation
  model,'' {\em PLOS Computational Biology}, \textbf{6}(1):e1000656.
\newblock Source code available at \url{GitHub.com/dlchao/FluTE},
  \doi{10.1371/journal.pcbi.1000656}

\bibitem{excel1}
Abir, M., Nelson, C., Chan, E.~W., Al-Ibrahim, H., Cutter, C., Patel, K., and
  Bogart, A. (2020) {\em {RAND} Critical Care Surge Response Tool: {An}
  Excel-Based Model for Helping Hospitals Respond to the {COVID-19} Crisis},
  RAND Corporation.
\newblock
  \url{www.rand.org/}\midurl{pubs/}\midurl{tools/}\midurl{TLA164-}\midurl{1.html}

\bibitem{excel2}
Alvarez, N.~M., Gonzalez-Gonzalez, E., and Trujillo-de Santiago, G. (2020)
  ``Modeling {COVID-19} epidemics in an excel spreadsheet: {Democratizing} the
  access to first-hand accurate predictions of epidemic outbreaks,'' {\em
  MedRxiv}.
\newblock Preprint, \doi{10.1101/2020.03.23.20041590}

@@

\bibitem{hci1}
Shneiderman, B., Plaisant, C., Cohen, M., and {\emph{et al}} (2016) {\em
  Designing the User Interface: Strategies for Effective Human-Computer
  Interaction}, Pearson, 6th~ed.
\newblock \url{www.cs.umd.edu/}\midurl{hcil/}\midurl{DTUI6}

@@

\bibitem{flexibility}
Hanson, C., and Sussman, G.~J. (2021) {\em Software design for flexibility: How
  to avoid programming yourself into a corner}, MIT Press.

@@

\bibitem{peerReview}
Baum, T., {Le\ss mann}, H., and Schneider, K. (2017) ``The choice of code
  review process: A survey on the state of the practice,'' {\em in Lecture
  Notes in Computer Science}, vol.~\textbf{10611} of Product-Focused Software
  Process Improvement: 18th International Conference, pp.~111--127.
\newblock \doi{10.1007/978-3-319-69926-4_9}

\bibitem{ssi-report}
Brett, A., Croucher, M., Haines, R., Hettrick, S., Hetherington, J., Stillwell,
  M., and Wyatt, C. (2017) {\em State of the Nation Report for Research
  Software Engineers}, Research Software Engineer Network.
\newblock \url{zenodo.org/}\midurl{record/}\midurl{495360#.Xyfuyi2ZOCM},
  \doi{10.5281/zenodo.495360}

@@

\bibitem{cyber-cacm}
Shostack, A., and Zurko, M.~E. (2020) ``Secure development tools and techniques
  need more research that will increase their impact and effectiveness in
  practice,'' {\em Communications of the ACM}, \textbf{63}(5):39--41.
\newblock \doi{10.1145/3386908}

@@

\bibitem{electronic-evidence}
Mason, S., and Seng, D. (2017) {\em Electronic Evidence}, Humanities Digital
  Library, 4th~ed.
\newblock (NB See
  \url{humanities-digital-library.org/index.php/hdl/catalog/book/electronicevidence}
  until DOI is resolved), \doi{10.14296/517.9781911507079}

\bibitem{simon-artificial}
Simon, H.~A., and Laird, J. (2019) {\em Sciences of the Artificial}, MIT Press,
  3rd~ed.

\bibitem{dunning-kruger}
Kruger, J., and Dunning, D. (1999) ``Unskilled and unaware of it: {How}
  difficulties in recognizing one's own incompetence lead to inflated
  self-assessments,'' {\em Journal of Personality and Social Psychology},
  \textbf{77}(6):1121--1134.
\newblock \doi{10.1037/0022-3514.77.6.1121}

\bibitem{dunning-kruger-numeracy}
Nuhfer, E., Fleisher, S., Cogan, C., Wirth, K., and Gaze, E. (2017) ``How
  random noise and a graphical convention subverted behavioral scientists'
  explanations of self-assessment data: {Numeracy} underlies better
  alternatives,'' {\em Numeracy}, \textbf{10}(1):4.
\newblock \doi{10.5038/1936-4660.10.1.4}

@@

\bibitem{viruses}
Thimbleby, H., Anderson, S.~O., and Cairns, P. (1999) ``A framework for
  modelling {Trojans} and computer virus infection,'' {\em Computer Journal},
  \textbf{41}(7):444--458.
\newblock \doi{10.1093/comjnl/41.7.444}

@@

\bibitem{lancet-retracted}
Mehra, M.~R., Desai, S.~S., Ruschitzka, F., and Patel, A.~N. (2020)
  ``{RETRACTED}: {Hydroxychloroquine} or chloroquine with or without a
  macrolide for treatment of {COVID}-19: {A} multinational registry analysis,''
  {\em The Lancet}, \textbf{{online}}:1--10.
\newblock \doi{10.1016/S0140-6736(20)31180-6}

\bibitem{fda}
Zhang, Y., Masci, P., Jones, P., and Thimbleby, H. (2019) ``User interface
  software errors in medical devices,'' {\em Biomedical Instrumentation {\&}
  Technology}, \textbf{53}(3):182--194.
\newblock \doi{10.2345/0899-8205-53.3.182}

\bibitem{stability}
Salama, M., Bahsoon, R., and Lago, P. (2021) ``Stability in software
  engineering: Survey of the state-of-the-art and research directions,'' {\em
  IEEE Transactions on Software Engineering}, \textbf{47}(7):1468--1510.
\newblock \doi{10.1109/TSE.2019.2925616}

@@

% expand generated/survey-references.bbl
% Generated by programs/data.js
\vbox{\bibitem{ref-1}
{Callahan, A., Steinberg, E., Fries, J. A., Gombar, S., Patel, B., Corbin, C. K., and Shah, N. H.} (2020) ``Estimating the efficacy of symptom-based screening for COVID-19,'' \emph{Nature Digital Medicine}, \textbf{3}(95):3pp.

\leftskip=\labelwidth
DOI \texttt{10.1038/s41746-020-0300-0}\\\hfill{Accessed 14 July 2020.}\ {Double-checked 17 January 2021}.}\bibskip

\vbox{\maprepo{MetricSelectionFramework}\bibitem{ref-2}
{Kanzler, C. M., Rinderknecht, M. D., Schwarz, A., Lamers, I., Gagnon, C., Held, J. P. O., Feys, P., Luft, A. R., Gassert, R., and Lambercy, O.} (2020) ``A data-driven framework for selecting and validating digital health metrics: use-case in neurological sensorimotor impairments,'' \emph{Nature Digital Medicine}, \textbf{3}(80):17pp.

\leftskip=\labelwidth
DOI \texttt{10.1038/s41746-020-0286-7}

{\url{github.com/ChristophKanzler/MetricSelectionFramework}}\\\hfill{Accessed 14 July 2020.}\ {Double-checked 17 January 2021}.}\bibskip

\vbox{\bibitem{ref-3}
{Roy, A., Nikolitch, K., McGinn, R., Jinah, S., Klement, W., and Kaminsky, Z. A.} (2020) ``A machine learning approach predicts future risk to suicidal ideation from social media data,'' \emph{Nature Digital Medicine}, \textbf{3}(78):12pp.

\leftskip=\labelwidth
DOI \texttt{10.1038/s41746-020-0287-6}\\\hfill{Accessed 14 July 2020.}\ {Double-checked 17 January 2021}.}\bibskip

\vbox{\bibitem{ref-4}
{Levine, D. M., Co, Z., Newmark, L. P., Groisser, A. R., Holmgren, A. J., Haas, J. A., and Bates, D. W.} (2020) ``Design and testing of a mobile health application rating tool.,'' \emph{Nature Digital Medicine}, \textbf{3}(74):7pp.

\leftskip=\labelwidth
DOI \texttt{10.1038/s41746-020-0268-9}\\\hfill{Accessed 14 July 2020.}\ {Double-checked 17 January 2021}.}\bibskip

\vbox{\bibitem{ref-5}
{Kannampallil, T., Smyth, J. M., Jones, S., Payne, P. R. O., and Ma, J.} (2020) ``Cognitive plausibility in voice-based AI health counselors,'' \emph{Nature Digital Medicine}, \textbf{3}(72):4pp.

\leftskip=\labelwidth
DOI \texttt{10.1038/s41746-020-0278-7}\\\hfill{Accessed 14 July 2020.}\ {Double-checked 17 January 2021}.}\bibskip

\vbox{\maprepo{PENet}\bibitem{ref-6}
{Huang, S., Kothari, T., Banerjee, I., Chute, C., Ball, R. L., Borus, N., Huang, A., Patel, B. N., Rajpurkar, P., Irvin, J., Dunnmon, J., Bledsoe, J., Shpanskaya, K., Dhaliwal, A., Zamanian, R., Ng, A. Y., and Lungren, M. P.} (2020) ``PENet a scalable deep-learning model for automated diagnosis of pulmonary embolism using volumetric CT imaging,'' \emph{Nature Digital Medicine}, \textbf{3}(61):9pp.

\leftskip=\labelwidth
DOI \texttt{10.1038/s41746-020-0266-y}

{\url{github.com/marshuang80/PENet}}\\\hfill{Accessed 14 July 2020.}\ {Double-checked 17 January 2021}.}\bibskip

\vbox{\bibitem{ref-7}
{Dhruva, S. S., Ross, J. S., Akar, J. G., Caldwell, B., Childers, K., Chow, W., Ciaccio, L., Coplan, P., Dong, J., Dykhoff, H. J., Johnston, S., Kellogg, T., Long, C., Noseworthy, P. A., Roberts, K., Saha, A., Yoo, A., and Shah, N. D.} (2020) ``Aggregating multiple real-world data sources using a patient-centered health-data-sharing platform,'' \emph{Nature Digital Medicine}, \textbf{3}(60):9pp.

\leftskip=\labelwidth
DOI \texttt{10.1038/s41746-020-0265-z}\\\hfill{Accessed 14 July 2020.}\ {Double-checked 17 January 2021}.}\bibskip

\vbox{\maprepo{PostoperativeOutcomes.RiskNet}\bibitem{ref-8}
{Hofer, I. S., Lee, C., Gabel, E., Baldi, P., and Cannesson, M.} (2020) ``Development and validation of a deep neural network model to predict postoperative mortality, acute kidney injury, and reintubation using a single feature set,'' \emph{Nature Digital Medicine}, \textbf{3}(58):10pp.

\leftskip=\labelwidth
DOI \texttt{10.1038/s41746-020-0248-0}

{\url{github.com/cklee219/PostoperativeOutcomes_RiskNet}}\\\hfill{Accessed 14 July 2020.}\ {Double-checked 17 January 2021}.}\bibskip

\vbox{\maprepo{philter-ucsf}\bibitem{ref-9}
{Norgeot, B., Muenzen, K., Peterson, T. A., Fan, X., Glicksberg, B. S., Schenk, G., Rutenberg, E., Oskotsky, B., Sirota, M., Yazdany, J., Schmajuk, G., Ludwig, D., Goldstein, T., and Butte, A. J.} (2020) ``Protected Health Information filter (Philter): accurately and securely de-identifying free-text clinical notes,'' \emph{Nature Digital Medicine}, \textbf{3}(57):8pp.

\leftskip=\labelwidth
DOI \texttt{10.1038/s41746-020-0258-y}

{\url{github.com/BCHSI/philter-ucsf}}\\\hfill{Accessed 14 July 2020.}\ {Double-checked 17 January 2021}.}\bibskip
